\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-03-20 paper/main.tex
.

While in this initial formulation the node-wise update step is defined
by the sum over all neighbouring node representations, we are able to
alter this formulation to another message passing scheme.  We are able
to rearrange the order of activation function $\sigma$, aggregation
$\mathrm{AGG}$ and linear neural layer $\mathrm{MLP}$ with this
formulation as proposed by \citet{GENConv2020}:
\begin{equation}
	\mathbf{x}_i^{\prime} = \mathrm{MLP} \left( \mathbf{x}_i +
	\mathrm{AGG} \left( \left\{
	\mathrm{\sigma} \left( \mathbf{x}_j + \mathbf{e_{ji}} \right) +\epsilon
	: j \in \mathcal{N}(i) \right\} \right)
	\right)
\end{equation}
where we will generally only consider
$\sigma \in \{\mathrm{ReLU}, \mathrm{LeakyReLU}\}$. We will denote
this generalized layer type as \textsc{GENConv}, following the
notation of PyTorch Geometric \cite{PytorchGeometric}.  While the
reordering is mainly import for numerical stability, this alteration
also addresses the vanishing gradient problem for deeper convolutional
networks \cite{GENConv2020}. Additionally, we can also generalize the
aggregation function to allow different weighting functions such as
learnable $\mathrm{SoftMax}$ or $\mathrm{Power}$ for the incoming
signals for each vertex, substituting the averaging step in
\textsc{GCNConv}. Hence, while \textsc{GCNConv} suffers from both
vanishing gradients and signal fading for large scale, highly
connected graphs, each propagation step in \textsc{GENConv} emphasizes
signals with values close to $0$ and $1$. The same convolutional
filter and weight matrix are applied to and learned for all nodes
simultaneously. % , and the resulting information\todo{Which information?
  % Specify} hold no information on their own connectivity.
We further employ another mechanism to avoid redundancy and fading
signals in stacked graph convolutional networks, using residual
connections and a normalization scheme \cite{DeepGCN2019,
  DeeperGCN2020}.
The residual blocks are reusable and can be stacked multiple times. %, thereby not losing focus of each node neighbourhood.
\todo[inline]{Needs a clearer outline/description/figure of YOUR model
structure.}
The structure is depicted in Figure~\ref{fig:ResGraphConvBlocks}.

>>>>

While in this initial formulation of a GCNConv the node-wise update
step is defined by the sum over all neighbouring node representations,
we can alter this formulation to other message passing schemes.  We
can rearrange the order of activation function $\sigma$, aggregation
$\mathrm{AGG}$, and linear neural layer $\mathrm{MLP}$ with this
formulation as proposed by \citet{GENConv2020}:
\begin{equation}
	\mathbf{x}_i^{\prime} = \mathrm{MLP} \left( \mathbf{x}_i +
	\mathrm{AGG} \left( \left\{
	\mathrm{\sigma} \left( \mathbf{x}_j + \mathbf{e_{ji}} \right) +\epsilon
	: j \in \mathcal{N}(i) \right\} \right)
	\right)
\end{equation}
where we only consider
$\sigma \in \{\mathrm{ReLU}, \mathrm{LeakyReLU}\}$. We denote
this generalized layer type as \textsc{GENConv} following the
notation of PyTorch Geometric \cite{PytorchGeometric}.  While the
reordering is mainly import for numerical stability, this alteration
also addresses the vanishing gradient problem for deeper convolutional
networks \cite{GENConv2020}. Additionally, we can also generalize the
aggregation function to allow different weighting functions such as
learnable $\mathrm{SoftMax}$ or $\mathrm{Power}$ for the incoming
signals for each vertex, substituting the averaging step in
\textsc{GCNConv}. Hence, while \textsc{GCNConv} suffers from both
vanishing gradients and signal fading for large scale and highly
connected graphs, each propagation step in \textsc{GENConv} emphasizes
signals with values close to $0$ and $1$. The same convolutional
filter and weight matrix are applied to and learned for all nodes
simultaneously. % , and the resulting information\todo{Which information?
  % Specify} hold no information on their own connectivity.
We further employ another mechanism to avoid redundancy and fading
signals in stacked graph convolutional networks, using residual
connections and a normalization scheme \cite{DeepGCN2019,
  DeeperGCN2020}.  The residual blocks are reusable and can be stacked
multiple times. The structure of the GNN architecture we use is shown
in Figure~\ref{fig:ResGraphConvBlocks}.
